\begin{definition}
	Let $R$ be a ring. A \emph{absolute value on $R$} is a function
	$|\cdot |: R \to \R^{+} \cup \{0\} $ satisfying for all $a, b \in R$
	\begin{enumerate}
		\item $|a| = 0 \iff a = 0$ 
		\item $|a \cdot b| = |a| \cdot |b|$ 
		\item $|a + b| \le |a| + |b|$
	\end{enumerate}
\end{definition}
\nomenclature[no]{$\mid \cdot\mid, \mid\mid \cdot \mid\mid $}{Norm or seminorm on a ring}
Note that if $R$ is not the zero ring, then $|1| = 1$ because $|1|^2 = |1| $ and $|1|\ne 0 $. 
\begin{example}
	The usual definition of absolute value on $\Z, \Q, \R$ is an absolute value. 
\end{example}
\begin{example}
	On any integral domain we can define the trivial absolute value as \[
	 |a| = \begin{cases}
		 1 & a \ne 0 \\
		 0 & a = 0
	 \end{cases}
	.\] 
\end{example}
\begin{example}
	A weirder absolute value on $\Z$ is the \emph{$p$-adic absolute value}, where $p$ is a prime. 
	Its defined as $|a|_p = p^{-n}$ where $n$ is the largest integers such that $p^{n} \mid a$, if $a \ne 0$ and $|0|_p = 0$. 


	This $p$-adic absolute value can be extended to an absolute value on $\Q$ by defining $|a / b|_p = \frac{|a|_p}{|b|_p}$. Let $\frac{a}{b}$ be any fraction. 
	We can think about this in the following way. 
	Factor out the largest powers of $p$ out of $a$ and $b$ and write $a = p^{n} a', b = p^{m} b'$. Then $\frac{a}{ b} = p^{n - m} \frac{a'}{ b'}$ and $|a / b|_p = p^{m - n}$. 
	So the $p$-adic absolute values only cares about what powers of $p$ occur and doesn't care about numbers coprime to $p $.
\end{example}
As we will see in \cref{sec:the_berkovich_spectrum_of_z}, we have essentially listed all absolute values on $\Z$ and $\Q$ as examples above.  
\begin{observation}
	A ring $R$ with an absolute value is a metric space with metric $d(x, y) = |x - y|$. 
\end{observation}
\nomenclature[d]{$d(x, y)$}{The metric on a metric space}
\begin{definition}
	A ring $R$ with an absolute value is \emph{complete} if all Cauchy sequences are convergent. 
\end{definition}
\begin{definition}
	Any ring $R$ with an absolute value can be completed, which is defined as \[
		\widehat{R} = \{(a_n)_n \text{ Cauchy sequence in } R\} / \sim
	\] 
	where two sequence $(a_n)_n, (b_n)_n$ are equivalent if $(a_n - b_n)_n \to 0$ as $n \to \infty$.
	Given  $a, b \in \widehat{R}$ with representatives $(a_n)_n, (b_n)_n$, the addition and multiplication are defined pointwise, i.e.\ \[
		a + b = [(a_n + b_n)_n], \quad a\cdot b = [(a_n \cdot b_n)_n]
	.\]
\end{definition}
\nomenclature{$\widehat R$}{The completion of the ring $R$}

Absolute values are a special case of (semi)norms
\begin{definition}
	Let $R$ be any ring. A \emph{seminorm on $R$} is a function $|\cdot |: R \to \R^{+} \cup \{0\} $ satisfying for all $a, b \in R$:
	\begin{enumerate}
		\item $|0| = 0, |1| = 1$,
		\item $|a \cdot b| \le |a| \cdot |b|$  (submultiplicativity),
		\item $|a + b| \le |a| + |b|$ (triangle inequality).
	\end{enumerate}
	A seminorm is called \emph{multiplicative} if it also satisfies a stronger version of 2. 
	\begin{enumerate}
		\item [4.]  $|a \cdot  b| = |a| \cdot |b|$.
	\end{enumerate}
\end{definition}
We will use the two notions interchangeably. 
Sometimes we will stress the fact that a seminorm might not be multiplicative and call it a \emph{submultiplicative norm}. 


Later in the thesis, when we work with Berkovich geometry, we will work with with finite type (semi)normed rings over some normed ground field. 
We need some compatibility between those two norms, i.e.\ we need a relative notion of norm. 
This is provided by the following definition. 
\begin{definition}
	Let $f: A \to B$ be a map of rings and suppose $A$ is equipped with a seminorm $|\cdot |_A$. 
	Then a seminorm $|\cdot |_B$ on $B$ is said to \emph{extend the seminorm on $A$} if \[
		|f(a)|_B = |a|_A, \quad \forall a \in A
	.\] 
\end{definition}

\begin{lemma}
	If $|\cdot |$ is a multiplicative seminorm on $R$ then  $|a | = |-a|$ for all $a \in R$. 
\end{lemma}
\begin{proof}
	We have $|a|^2 = |a^2| = |-a|^2$. As all norms are positive we find that $|a| = |-a|$. 
\end{proof}


\begin{definition}
	The \emph{kernel} of a seminorm $|\cdot |: R \to \R^{+}$ is defined as \[
		\ker(|\cdot |) = \{a \in \R \st |a| = 0\} 
	.\] 
\end{definition}
\begin{remark}\label{rem:ker_norm_ideal}
	Let $ |\cdot |$ be a norm on $R$. Then $\ker |\cdot |$ is an ideal of $R$. If $|\cdot |$ is multiplicative then $\ker |\cdot |$ is even a prime ideal!
\end{remark}
\begin{proof}
	Let $a, b \in \ker |\cdot |, c \in R$. Then $0 \le |a + b| \le |a|+|b| = 0$. So  $a + b \in \ker |\cdot |$. 
	Also $0 \le |c \cdot a| \le |c|\cdot |a| = 0$. So $c \cdot a \in \ker |\cdot |$. 
	This shows that $\ker |\cdot  |$ is an ideal. 
	
	Suppose that $|\cdot |$ is multiplicative. 
	Let $a, b\in R $ such that $a\cdot b \in \ker |\cdot |$ then  $|a|\cdot |b| = |a\cdot b| = 0$. 
	Hence either $|a| = 0$ or  $|b|=0$. 
	So either  $a \in \ker |\cdot |$ or $b \in \ker |\cdot |$. 
\end{proof}


\begin{definition}
	Let $R$ be a ring and $|\cdot |$ a seminorm on $R$. 
	Then $|\cdot |$ is called a \emph{norm} if $\ker |\cdot | = 0$, i.e.\ $|a| = 0 \iff a = 0$. 
\end{definition}

So an absolute value is a multiplicative norm. 

\begin{lemma}
	Any seminorm $|\cdot |$ on a field $F$ is a norm, i.e.\ has trivial kernel. 
\end{lemma}
\begin{proof}
	We have that $|1| = 1$. So $1 \not\in \ker |\cdot |$ and thus $\ker |\cdot |$ is an ideal of $F$ different from $F$. 
	As $F$ is a field this means that $\ker |\cdot | = (0)$. So $|\cdot |$ is norm. 
\end{proof}

\subsection{Non-Archimedean rings and fields} \label{sec:non-archimedean_rings_and_fields}
\begin{definition}
	A (semi)norm $|\cdot |$ on $R$ is called \emph{non-archimedean} if it satisfies the following stronger version of the triangle inequality, \[
	\forall a, b \in R: |a + b| \le \max \{|a|, |b|\} 
	.\] 
	A \emph{archimedean (semi)norm} is a norm that is not non-archimedean.
\end{definition}

\begin{definition}
	A \emph{non-archimedean ring} (resp.\ \emph{field}) is a ring (resp.\ field) equipped with a multiplicative non-archimedean norm. 
\end{definition}

One might wonder why there is a negation in the name of non-archimedean norms, as they are defined by having some extra property that archimedean norms do not have. 
It is related to the archimedean principle that states that for any real value $a$, there is some integer $r$ such that $|r| > |a|$. 
The following exercise should make clear why non-archimedean rings, are from this perspective really not archimedean.
\begin{exercise}[{\cite[ex.\ 1.3.1]{nicaiseNonarchimedeanGeometry2017}}]
	Let $k$ be a field.
	Show that a multiplicative seminorm $|\cdot |$ on $k$ is non-archimedean if and only if the image of $\Z$ in $k$ is bounded. 
\end{exercise}
\begin{proof}
	Suppose $|\cdot |$ is non-archimedean. Then for any positive integers $n$ we have \[
	|n| = \left|\sum_{i = 1}^{n} 1 \right| \le \max \{1, 1, \ldots, 1\}  = 1
	.\] 
	And for negative integers we have $|n| = |-n| \le 1$. So $\|\cdot \|$ is bounded on the image of $\Z$ by $1$. 


	Suppose that $|\cdot |$ is bounded on the image of $\Z$ by $c$. 
	Let $x, y \in k$. Then \[
		|(x + y)^{n}| = \left| \sum_{i = 0}^{n} \binom{i}{n} x ^{i} y ^{n-i}\right| \le (n + 1)\cdot c \max(x, y)^{n}
	.\] 
	So \[
		|x + y| \le \sqrt[n]{c\cdot (n + 1)}  \max(x, y)
	.\] 
	Taking $n \to \infty$ yields the non-archimedean triangle inequality. 
\end{proof}

\begin{corollary}
	Let $A \subset  B$ an inclusion of rings  equipped with multiplicative norms such that the norm on $B$ extends the norm on $A$. 
	Then $A$ is non-archimedean if and only if $B$ is non-archimedean. 
\end{corollary}

\begin{remark}
	Suppose $R$ is a multiplicative non-archimedean norm and we have $a, b \in R$ such that $|a| \ne |b|$ then the triangle inequality is an equality \[
	|a + b| = \max \{|a|, |b|\} 
	.\] 
	So in some sense equality is the generic case. 
\end{remark}
\begin{proof}
	Suppose without loss of generality that  $|a| > |b|$, and assume by contradiction that $|a + b| < \max \{|a|, |b|\}  = |a|$. 
	Then \[
		|a| = |(a + b) - b| \le \max \{|a + b|, |- b|\} = \max \{|a + b|, |b|\}  
	.\] 
	But this contradicts that $|a| > |b|$ and $|a| > |a + b| $. 
\end{proof}
The non-archimedean triangle inequality sounds like a really strong property and thus it might seem that not many norms will be non-archimedean. 
But as you will see in this thesis, most norms that pop up are non-archimedean. 
In fact the only complete valued fields with archimedean norms are $\R$ and $\C$.\footnote{This is a consequence of Gel'fand-Mazur theorem and Ostrowki's classification (see \cref{thm:ostrowksi}) of norms on $\Q$.}



Note that the definition a non-archimedean norm only depends on the multiplicative structure on $\R^{+}$ and no longer depends on the additive structure. 
Sometimes it is more natural define norms in terms the isomorphic group $\R, +$ (and add $\infty$ instead of $0$ to the group). 
These are typically called valuations. 


\begin{definition}
	Let $R$ be a ring. A \emph{valuation on $R$} is a function $v:R \to \R \cup \{\infty\} $ such that 	
	\begin{itemize}
		\item $v(0) = \infty$, $v(1) = 0$. 
		\item $v(a\cdot b) = v(a) + v(b)$
		\item $v(a + b) \le \min\{v(a), v(b)\}$
	\end{itemize}
\end{definition}
\nomenclature[v]{$v$}{Valuation on a ring}

\begin{remark}
	Note that there is essentially no difference between a non-archimedean absolute value and a valuation because because they are in bijective correspondence with one another.  Any absolute value $|\cdot |$ defines a valuation $x \mapsto -\log |x|$ and given a valuation $v$ one defines a non-archimedean absolute value $x\mapsto e^{- v(x)}$. 
	We will use the two notions interchangeably. 
\end{remark}


\begin{definition}
	A valuation $v: R \to \R \cup \{\infty\} $ is \emph{discrete} if its image is contained in $\alpha \cdot \Z$ for some $\alpha \in \R$. 

	A norm on  $R$ is \emph{discrete} if its associated valuation is discrete.
\end{definition}
If the valuation $v$ on $R$ is non-trivial and discrete, then it is easy to see that $v(R)$ is either $\alpha \cdot \Z$ or $\alpha \cdot \Z_{\ge 0}$ for some $\alpha \in \R_> 0$. 
Usually, but not always, it is convention to scale $v$ such that $\alpha = 1$. 



\begin{theorem}\label{thm:norm_finite_field_ext}
	If $L$ is a finite field extension of a complete non-archimedean field $K$, then there is a unique extension of the norm of $K$ to $L$. Moreover, this extension is also non-archimedean.
\end{theorem}
\begin{proof}
	This a very technical result and for the proof we refer to \cite[][appendix A]{boschLecturesFormalRigid2014}. 
\end{proof}
\begin{corollary}
	If $K$ is a complete non-archimedean field then the norm of  $K$ extends uniquely to its algebraic closure $\overline{K}$.
\end{corollary}
\nomenclature[bar]{$\overline{k}$}{Algebraic closure of $k$}
\begin{proof}
	Recall that \[
	\overline{K} = \varinjlim_{L \supset K} L
	,\] 
	where $L$ ranges over all algebraic extensions of $K$. 
	As all these algebraic extensions have unique norms extending  the norm on $K$ and for $L_1 \supset L_2 \supset K$ the norm on  $L_1$ must restrict to norm on $L_2$ by uniqueness. 
	It is clear that the norm functions $L \to \R^{+} \cup \{0\} $ glue to a map $\|\cdot \|: \overline{K} \to \R^{+} \cup \{0\} $. 

	It is easy to verify that this is a norm on $\overline{K}$ extending the norm on $K$. 
\end{proof}

\begin{theorem}
	[Krasner's Lemma]
	Let $K$ be a non-archimedean algebraically closed field. 
	Then its completion, $\widehat K$ is algebraically closed as well. 
\end{theorem}
\begin{proof}
	This follows from the continuity of roots. See \cite[][lem A.6]{boschLecturesFormalRigid2014} for a detailed argument. 
\end{proof}

This shows that we can canonically turn any non-archimedean field $K$ into an algebraically closed and complete field in a canonical way by considering $\widehat{\overline{K}}$, which is first taking the algebraic closure of $K$ and then completing it. 

\begin{definition}
	For a prime $p$ we define the \emph{p-adic complex numbers} as \[
	\C_p = \widehat{\overline{\Q_p}}
	.\] 
\end{definition}
\nomenclature[Cp]{$\C_p$}{$p$-adic complex numbers}

This is useful because in some contexts Berkovich geometry works best when the base field is algebraically closed and complete. 
So $\C_p$ is a sort of algebraically closed version of the $p$-adics. 

\begin{definition}
	Let $R$ be a non-archimedean ring. We write 
	\begin{align*}
		R^{o} &= \{a \in k \st |k| \le 1\}  \\
		R^{oo} &=  \{a \in k \st |k| < 1\}  \\
		\widetilde R &= R^{o} / R^{oo}
	.\end{align*}
\end{definition}

If $k$ is a field then $k^{0}$ is a valuation ring and $ k^{00}$ is its maximal ideal. 
We will usually write $K$ for a non-archimedean field with non-trivial norm, $R = K^{0}$ for its valuation ring, $k = \widetilde K$ for its residue field. 

\begin{definition}
	Let $K$ be a non-archimedean field. 
	The \emph{value group of $K$} is \[
	|K^{\times }| = \{|a| \st  a \in K^{\times }  \} 
	.\] 
	This is a subgroup of $(\R^{ +}, \cdot )$. 
\end{definition}
\nomenclature[vg]{$\mid K^{\times }\mid$}{Value group of $K$}
