In this thesis we study the relation between the reduction type and the topology of the Berkovich analytification of elliptic curves over complete discretely valued fields. 
We study an elliptic curve $E$ by considering its double cover of the projective line $f:E \to \pro^{1}_K$.
Central in this discussion are weight functions and the essential skeleta of analytification of curves. 
These concepts are only recently developed by Johannes Nicaise and Mircea Mustaţă \cite{mustataWeightFunctionsNonArchimedean2015}.

Our goal is twofold. We aim to obtain a more geometric understanding of the reduction of elliptic curves using tools from Berkovich geometry, in particular weight functions and skeleta. 
Conversely by using classical tools, in particular Tate's algorithm to understand the reduction type of an elliptic curve, we aim to gain a better understanding of weight functions and the essential skeleton. 
Especially in the case where the resiude characteristic of the ground field is $2$, the situation is less clear.
Then $f: E \to \pro^{1}_K$ is a wildly ramified cover, and the behavior of weight functions under such maps is currently not understood well.  

\medskip

Special thanks goes out to my supervisor, Johannes Nicaise, who suggested this project to me and guided me very well on this journey towards research mathematics. 
I also want to thank Art Waeterschoot for his help in coming up with the research question and always being available to discuss ideas. 
Finally I want to thank Nick Shamaiev for being a great study partner and the many hours we spend trying to wrap our heads around Berkovich geometry. 


