In the case where $\ch k \ne 2$ we can use \cref{prop:weightfunction_fullback} to compare the skeleton $\sk(\mathscr P)$ with the essential skeleton $\sk(E)$. 
\begin{lemma}\label{lem:sk_E_pulls_back}
	Let $\mathscr P$ be as in \cref{sec:a_weight_function_on_pro_1_k}, and $E$ from \cref{prob:main_problem}. 
	Then \[
		\sk(E) = \phi^{-1}(\sk(\mathscr P))
	.\] 
\end{lemma}
\begin{proof}
	In \cref{prop:model_P_is_KS} we saw that $\sk(\mathscr P) = \sk(\pro^{1}_K, \sigma)$, where $\sigma$ is the rational section of $\omega_{\pro^{1}_K}^{\otimes 2}$ with poles at $0, 1, \lambda, \infty$, which is unique up to multiplication by $K$. 
	Then $f^* \sigma$ is a $2$-pluricanonical form. 
	Indeed, we can take $\sigma$ as a global section of $\omega_{\pro^{1}_K}^{\otimes 2}(f_* \ram _f)$. 
	And 
	\[
		f^* (\omega_{\pro^{1}_K / K}^{\otimes 2}(-f_* \ram _f)) = \omega_{E /K}^{\otimes 2} \otimes \mathcal{O}(2 \ram_f) \otimes f^*f_* \mathcal{O}(-\ram _f) = \omega_{E / K}
	.\] 
	We also have 
	\[
		\sk(E, f^*\sigma) = \minloc \wt_{f^* \sigma} = \minloc \wt_{\sigma}\circ \phi = \phi^{-1}(\minloc \wt_\sigma) = \phi^{-1} (\sk(\pro^{1}_K, \sigma))
	.\] 
	Recall that $\omega_{E / K}$ is trivial as $E$ is an elliptic curve. 
	So all pluricanonical forms are the same up to multiplication. 
	So $\sk(E)$ can be computed using only one pluricanonical form, thus \[
		\sk(E) = \sk(E, f^*\sigma) = \phi^{-1}(\sk(\pro^{1}_K, \sigma)) = \phi^{-1}(\mathscr P)
	.\] 
\end{proof}

\subsection{The semistable case} \label{sec:the_semistable_case}
\input{tame_semistable.tex}

\subsection{Determining $m$ when $E$ is of type $\mathrm I_m^*$} \label{sec:determining_m_when_e_is_of_type_ims}
\input{tame_type_Is.tex}

\subsection{Distinguishing between $\mathrm I_m$ and  $\mathrm I_m^*$} \label{sec:distinguishing_between_im_and_ims}

Recall that $E$ is given by the Weierstrass equation 
\begin{equation}\label{eq:weierstrass_dist}
	E: y^2 = x(x-1)(x-\lambda)
,\end{equation}
with $\lambda = u \cdot \pi^{n}$ and $u$ some unit in $R$. 
If $n \ge 0$ we found that this Weierstrass equation is minimal in  \cref{sec:char_k_is_not_2}.
So the component of the Weierstrass model is a multiplicity 1 component of $\mathscr E_\text{min} $, the minimal snc-model. 
Let $w$ be the divisorial point associated to component.
If we consider the morphism of models (on affine charts) \[
	\spec \frac{R[x, y]}{(y^2 - x(x-1)(x-\lambda)} \to \spec R[x]
\]
we see that the map dominates on the special fiber. 
So $\phi(w)$ is the point corresponding to the disk $B(0, 1)$ (\cref{lem:model_disk_proj_line})
But this exactly the point $b$. So $\phi(w) = b$ and in particular $w \in \phi^{-1}(\mathscr P) \in \sk(E)$. 
So $w$ is a multiplicity 1 essential component of $\mathscr E_\text{min} $.
This can only be the case if $E$ is of type $\mathrm I_{m}$ for some $m \ge 0$. 
As a bonus we also see that when $n = 0$,  $E$ is of type $I_0$ and not of some other reduction type with $\sk(E)$ a point. 

Putting all information in this section together we have reached obtained an alternative and almost purely Berkovich geometric proof for \cref{prop:conclusion_tate_tame}, the conclusion of Tate's algorithm. 
\medskip

In \cref{rem:justification_semistable} we said that when $n < 0$ we that whether $E$ is semistable depends on the parity of $n$. 
Here is a (conjectural) explanation for this. 
When $n < 0$, the Weierstrass equation \eqref{eq:weierstrass_dist} is no longer defined over $R$. 
After performing a coordinate transformation $(x_{2i}, y_{3i}) = (\pi^{-2i}x, \pi^{-3i}y)$ with $i = \left\lceil \frac{n}{2} \right\rceil $, the Weierstrass equation becomes \[
	E: y_{3i}^2 = x_{2i}(x_{2i}-\pi^{i})(x_{2i} - \pi^{i}\lambda)
.\] 
This Weierstrass equation is defined over $R$ and conjecturally minimal. 
Again let $w$ be the divisorial point associated to this Weierstrass model. 
From a similar map of models \[
	\spec \frac{R[x_{2i}, y_{2i}]}{\left(y_{3i}^2 - x_{2i}(x_{2i}-\pi^{i})(x_{2i} - \pi^{i}\lambda)\right)} 
	\to \spec R[x_{2i}]
,\] 
we see that $\phi(w)$ is the disk $B(0, |\pi|^{-n})$ if $n$ is even and $B(0,|\pi|^{-n-1}) $ when $n$ is odd. 
For this configuration of $\Gamma_\lambda$ (recall \cref{fig:configurations_of_gamma_lambda}) we can also construct a similar model $\mathscr P'$ of $\pro^{1}_K$ whose skeleton is the line from $B(0, 1)$ to $B(0, |\pi|^{-n})$ and such that $\sk(E) = \phi^{-1}(\sk(\mathscr P'))$.
In particular $w \in \sk(E)$  if and only if $i$ is even. 
So when $i$ is even the Weierstrass component is essential, thus the reduction type is $\mathrm I_m$ for some $m$. 
And when  $i$ is odd, the Weierstrass component is inessential. 
So the reduction type of $E$ is $\mathrm I_m^*$ for some $m$. 





