In this section we will describe the category of $K$-analytic spaces, which is where the Berkovich spaces of schemes will live. 
The main building blocks of these spaces are affinoid algebras which are a type of complete $K$-algebras. 
These will also be  crucial for defining the structure sheaf on Berkovich spaces. 

\subsection{Banach Algebras} \label{sec:banach_algebras}
\begin{definition}
	A $K$-Banach space is a $K$-vector space equipped with a norm that is complete with respect to that norm. 
\end{definition}

\begin{definition}
	Let $A, B$ be $K$-Banach spaces. 
	A $K$-vector space morphism $\phi: A \to B$ is \emph{bounded} if there is some $C\in \R$ such that $\|\phi(a)\|\le C \|a\| $. 
\end{definition}

\begin{lemma}
	A morphism $A \to B$ is bounded if and only if it is continuous. 
\end{lemma}

\begin{definition}
	A Banach $K$-algebra, $A$, is a commutative, associative, unital $K$-algebra with a submultiplicative norm that is a $K$-Banach space.
\end{definition}
\begin{definition}
	Let $A$ be a $K$-algebra. 
	Two norms $\|\cdot \|_1, \|\cdot \|_2$ on $A$ are called equivalent if and only if they induce the same topology. 

	This means that there are non-zero constants $C, C'$ such that for every $ a\in A$ we have $C\|a\|_1 \le \|a\|_2 \le C'\|a\|_1$. 
\end{definition}

\begin{definition}
	Let $A$ be an $K$-Banach algebra and $I$ be a closed ideal in $A$. 
	Then we define the \emph{residue norm} on $A / I$ as 
	\begin{align*}
		\|\cdot \|_\text{res} : A / I &\longrightarrow \R \\
		a + I &\longmapsto \inf_{x \in a + I} \|x\|
	.\end{align*}
\end{definition}

To describe the category of $K$-Banach algebras we still need morphisms.
\begin{definition}
	Let $A, B$ be $K$-Banach algebras. 
	A $K$-algebra morphism $\phi: A \to B$ is \emph{admissible}  if the induced map $A / \ker \phi \to \im \phi$ is a homeomorphism, where $A / \ker \phi$ is equipped with the residue norm and $\im \phi$ with subspace norm of $B$. 
\end{definition}

\begin{remark}\label{rem:uniqueness_norm_banach_algebra}
	Note that the identity  $\id: (A, \|\cdot \|_1) \to (A, \|\cdot \|_2)$ between two Banach $K$-algebras is a isomorphism in the category of $K$-Banach spaces if and only if the norms $\|\cdot \|_1, \|\cdot \|_2$ are equivalent. 
	So the norm is not intrinsic to an equivalence class of objects in the category of Banach  $K$-algebras, but it is well defined up to equivalence. 
\end{remark}

There is also a good way to equip the tensor product of Banach $K$-algebras with a submultiplicative norm, turning it again into a Banach $K$-algebra.
\begin{definition}
	Let $A, B, C$ be Banach $K$-algebras with morphisms  $C\to A, C \to B$. Then the \emph{completed tensor product}, written $A \widehat \otimes_C B$, is the completion of the ordinary tensor product $A \otimes_C B$ with norm defined by \[
		\|x\| = \inf \left\{\max_{i = 1}^{n} |a_i||b_i|  \st n \in \N, a_i \in A, b_i \in B, x = \sum_{i = 1}^{n} a_i \otimes_C b_i\right\} 
	\] 
	for any $x \in A \otimes_C B$. 
\end{definition}
\nomenclature[Ox]{$A \widehat \otimes_C B$}{The completed tensor product of $A$ and $B$ over $C$}

\begin{proposition}\label{prop:universal_prop_complete_tensor}
	The completed tensor product, like the tensor product for rings, is the pushout of the diagram $A \leftarrow C \to B$ in the category of  $K$-Banach algebras. I.e.\ it satisfies the universal property that for any  $D$ and morphism $A \to D$,  $B \to D$ making the square with $C$ commute there exists a unique map $A \widehat\otimes_C B \to D$ making the diagram commute\[
	\begin{tikzcd}
		C \rar \dar & A \dar \ar[bend left]{rdd} \\
		B \rar \ar[bend right]{drr} &  A \widehat{\otimes}_C B \ar[dashed]{dr}{\exists !} \\
		 & & D
	\end{tikzcd}
	.\] 
\end{proposition}
\begin{proof}
	See \cite[][section 2.1.7]{siegfriedboschNonArchimedeanAnalysisSystematic1984}. 
\end{proof}

\subsection{Berkovich spectra of Banach algebras} \label{sec:berkovich_spectra_of_banach_algebras}


To an affinoid algebra we can also associate a Berkovich space, which will be sligtly differently defined than our adhoc definition from \cref{sec:berkovich_spaces} for any space, because we need to introduce the concept of a bounded norm.

\begin{definition}
	Let $(A, \|\cdot \|)$ be a Banach $K$-algebra. Another norm $\|\cdot \|'$ on $A$ is \emph{bounded}  if there is some constant $C$ such that  $\|a\|' \le C \|a\|$ for all $a \in A$. 
\end{definition}


\begin{remark}
	If $\|\cdot \|'$ is multiplicative then we may assume the constant $C$ to be $1$. 
	I.e.\ a multiplicative norm $\|\cdot \|'$ is bounded if and only if  for all $a \in A: \|a\|' \le \|a\|$. 
\end{remark}
\begin{proof}
	For any $n \in \N, a \in A$ we find $\|a^{n}\|' \le C \|a^{n}\| \le C \|a\|^{n}$. 
	Taking the $n$'th root yields \[
		\|a\|' \le \sqrt[n]{C} \|a\|
	.\] 
	Taking the limit $n \to \infty$ yields the desired inequality. 
\end{proof}

\begin{definition}\label{def:spectrum_banach_algebra}
	Let $(A, \|\cdot \|)$ be a Banach $K$-algebra. 
	The Berkovich spectrum (as a topological space) is \[
		\mathcal{M} (A) = \{x: A \to\R^{+} \cup \{0\}  \st x \text{ is a bounded multiplicative seminorm}\} 
	\] 
	equipped with the coarsest topology that makes all maps $\mathcal{M} (A) \to [0, \infty): x \mapsto |f|_x$ for any $f \in A$ continuous. 
\end{definition}
Note that the space $\mathcal{M} (A)$ is unaffected if we equip $A$ with a different but equivalent norm. 
So by \cref{rem:uniqueness_norm_banach_algebra}, the functor $\mathcal{M}$ is actually well defined as up to isomorphism $\mathcal{M} (A)$ only depends on the equivalence class of $A$ in the category of Banach $K$-algebras.

It may seem odd that in \cref{def:spectrum_banach_algebra} we do not require $x$ to extend the norm on $K$. 
This is because it is actually a consequence of the condition that $x$ is bounded. 

\begin{proposition}\label{prop:norm_spectrum_extends_base_field}
	Every norm in $\mathcal{M} (A)$ extends the norm on $K$. 
\end{proposition}
\begin{proof}
	Suppose $(A, \|\cdot \|)$ is a Banach $K$-algebra. 
	Let $x \in \mathcal{M} (A)$ be a norm. 
	Then for any $\lambda \in K, \lambda \ne 0$ we have $|\lambda|_x \le  \|\lambda\cdot 1\| = |\lambda| \cdot \|1\| = |\lambda|$. 
	Similarly $|\lambda|_x^{-1} = |\lambda^{-1}|_x  \le |\lambda^{-1}| = |\lambda|^{-1}$. 
	From this it follows that $|\lambda|_x = |\lambda|$
\end{proof}


\begin{proposition}
	$\mathcal{M} (A)$ is non-empty. 
	In particularly for every maximal ideal $\mathfrak{m}  \subset  A$ there is a norm $x \in \mathcal{M} (A)$ such that $\ker x = \mathfrak{m} $.
\end{proposition}
\begin{proof}
	Let $\mathfrak{m}$ be a maximal ideal of $A$. 
	Then $\frac{A}{\mathfrak{m} }$ is a field  with at least one submultiplicative norm induced by the norm on  $A$. 
	So the set of submultiplicative norms on  $A/\mathfrak{m} $ is non-empty and may be partially ordered by $|\cdot |_1 \le |\cdot |_2$ if $|a|_1 \le |a|_2$ for all $a \in A / \mathfrak{m} $. 

	So by Zorn's lemma there is a minimal such norm $|\cdot |_\text{min} $ on $\mathcal{A}  / \mathfrak{m} $. 
	I claim that this norm is multiplicative. 
	First we will show that $|\cdot |_\text{min} $ is power multiplicative. 
	Define $\rho(a) = \lim_{n \to \infty} \sqrt[n]{|a^{n}|_\text{min} } $. Then $\rho$ is powermultiplicative and $\rho \le |\cdot |_\text{min} $. Hence $\rho = |\cdot |_\text{min} $. 

	Now we will show that $|f^{-1}|_\text{min}  = |f|^{-1}_\text{min} $ for any $f \ne 0$. 
	Suppose that this isn't the case. Let  $r = |f^{-1}|^{-1} < |f|$. 
	Define \[
	B = \left\{b = \sum_{i = 0}^{\infty} a_i T^{i}\st \|b\|  =\sup |b_i|_\text{min}  r^{i} < \infty\right\} 
	.\] 
	We will see in the next section that this is a Banach algebra. Then $(T - f)^{-1} = f^{-1}\sum_{i = 0}^{\infty} (f^{-1} T)^{i} \not\in B $. So $T - f$ is not invertible, and in particular $(T - f)$ is a closed ideal. 
	Hence we can define $A' = B / (T - f)$ equipped with the residue norm. 
	This gives contractive morphisms  $A \to B \to A'$ and we can pull back the norm on $\|\cdot \|$ on $A'$ to $A$. 
	Note that $\|f\| = \|T\|  \le  r < f$. So $\|\cdot \|$ contradicts the minimality of $|\cdot |_\text{min} $

	Now we can easily show that $|\cdot |_\text{min} $ is multiplicative. 
	Let $f, g \ne 0$ be elements in $A / \mathfrak{m} $, then \[
		|fg| \le |f|\cdot |g| \le (|f^{-1}| \cdot |g^{-1}|)^{-1} \le |(fg)^{-1}|^{-1} = |fg|. 
	\]
	We can now pull back $|\cdot |_\text{min} $ to $A$ which yields the desired norm. 
\end{proof}

\begin{corollary}\label{cor:non_vanish_invertible}
	An element $a \in A$ is invertible if and only if $|a|_x > 0, \forall x \in \mathcal{M} (A)$.
\end{corollary}
\begin{proof}
	\ltr
	Suppose $a $ is invertible. Then for any  $x \in \mathcal{M} (A)$ we have that $1 = |1|_x = |a^{-1}a|_x = |a|_x |a^{-1}|_x$, from which it is clear that $|a|_x \ne 0$. 

	\rtl Suppose $a$ is not invertible. Then there is some maximal $\mathfrak{m}  $ ideal containing $a$. 
	By the previous proposition there is some $x \in \mathcal{M} (A)$ such that $\ker x = \mathfrak{m} $ and thus $|a|_x = 0$. 
\end{proof}

\begin{proposition}
	The topology on $\mathcal{M} (A)$ is Hausdorff and compact. 
\end{proposition}
\begin{proof}
	Hausdorff is proven in exactly the same way as \cref{prop:spec_ring_haussdorf}.
	For compactness see \cite[][thm.\ 1.2.1]{berkovichSpectralTheoryAnalytic2012}.
\end{proof}
\subsection{Affinoid algebras} \label{sec:affinoid_algebras}
To further develop the theory we need to restrict the category of Banach algebras to those that are ``finitely generated'' in some appropriate sense. 

\begin{definition}
	[2.1.2, \cite{conrad2008several}]
	Let $A$ non-archimedean ring and $r_1, \ldots, r_n$ some positive real numbers. We define \[
		A \left<r_1^{-1}t_1, \ldots, r_{n}^{-1} t_n \right> = \left\{\sum_{\nu \in \N^{n}}^{} a_\nu t^{\nu} \in A[[t_1,\ldots, t_n]]\st a_\nu r^{\nu} \to 0, \text{ as } \nu \to \infty\right\} 
	.\] 
\end{definition}
This can be thought of as the completing of the polynomial ring $A[x_1, \ldots, x_n]$ with the norm defined as 
\begin{equation}\label{eq:norm_tate}
	\left\| \sum_{\nu \in \N^{n}} a_\nu y^{\nu}\right\| = \max_{\nu \in \N^{n}} \|a_\nu r^{\nu}\|
\end{equation}
This gives a similarly defined norm on $A\left<y_1, \ldots, y_n \right>$, but there are many other interesting norms on $A \left<y_1, \ldots, y_n \right>$, as we will discover. 



\begin{definition}
	A \emph{Tate algebra} in $n$ variables is the ring \[
		T_n(K) = K\left<T_1, \ldots, T_n \right>
	,\]
	equipped with the norm as in \eqref{eq:norm_tate}.
\end{definition}
\nomenclature[affinoid]{$A\left<\overline{r}^{-1} \overline{T} \right>$}{The affinoid extension of $A$}
\nomenclature[Tate]{$T_n(K)$}{The tate algebra over $K$ in $n$ variables}

Similarly to polynomial rings, these Tate algebras are \emph{free} in a sense made precise by the following proposition. 
\begin{proposition}\label{prop:universal_property_tate_algebars}
	Take $r_1, \ldots, r_n \in \R^{ +}$ and let $A$ be a $K$-Banach algebra. 
	The map
	\begin{align*}
		\Phi: \hom(K\left<\underline r^{-1} \underline T \right>, A) &\longrightarrow \prod_i A_{\le r_i}  \\
		f &\longmapsto (f(T_1), \ldots, f(T_n))
	\end{align*}
	is a well defined isomorphism. 
	Here the hom-set is in the category of $K$-Banach algebras and $A_{\le r} = \{a \in A \st (r^{-n}|a^{n}|)_n \text{ is bounded}\} $
\end{proposition}
\begin{proof}
	Let's first check that the map is well defined. 
	Let $f: K\left<\underline r^{-1} \underline T \right> \to A$ be such a map. 
	We need to check that $|f(T_i)| \le r_i$. 
	Suppose that  $|f(T_i)| > r_i$, then there is some $a \in K$  and $m \in \N$ such that $|f(T_i)^{m}| > |a| > r_i^{m}$. 
	We know that $(a^{-1}T_i^{m})^{j} \mapsto 0$ as $j \to \infty$, but $|a^{j} f(T_i^{m})^{j}| \to \infty $, which contradicts the continuity of $f$. 


	As $K[\underline T]$ is dense in $K\left<\underline r^{-1} \underline T \right>$, $f$ is uniquely determined by its restriction to $K[\underline T]$. So $\Phi$ is injective, as polynomial rings are free.
	To check that $\Phi$ is surjective, it is sufficient to note that for any $a = \sum_{\nu \in \N^{n}}^{} a_\nu \underline T^{\nu}$ with $r^{\nu} |a_\nu| \to 0$ the series $\sum_{\nu \in \N^{n}} a_\nu f(T^{\nu})$ is convergent in $A$. 
\end{proof}


\begin{definition}
	A affinoid algebra is a $K$-algebra $A$ with such that there is an admissible surjective morphism $f: K\left<\underline r ^{-1} \underline T \right> \to A$ for some $\underline r = (r_1, \ldots, r_n)$. 

	An affinoid algebra is said to be \emph{strict} if it admits such morphism with $r_i  \in |K^{\times }|$ for all $i$. 
	For any group $H$, with $|K^{\times }| \subset  H \subset \R^{ +}$ the algebra $A$ is said to be \emph{$H$-strict} if and it admists such morphism with $r_i \in H$ for $i$. 
\end{definition}
This means that $A$ can be written as $K\left<r_1^{-1}T_1, \ldots, r_n^{-1}T_n \right> / I$ where $I$ is some (closed) ideal.
This does not mean that $A$ necessarily comes equipped with the residue norm, but this doesn't matter as the open mapping theorem shows that the norm on $A$ must be equivalent to residue norm.


\begin{proposition}
	Affinoid algebras are Noetherian and all ideals are closed. 
\end{proposition}
\begin{proof}
	See \cite[][chap.\ 6 prop.\ 3]{siegfriedboschNonArchimedeanAnalysisSystematic1984} for the case of strict affinoid algebras and \cite[][prop.\ 2.1.3]{berkovichSpectralTheoryAnalytic2012} for how to extend that result general affinoid algebras. 
\end{proof}

\subsection{Affinoid domains} \label{sec:affinoid_domains}

In order to turn $\mathcal{M} (A)$ into a ringed space and define a structure sheaf we need an analogue of affine opens on which we know what the sections of the structure sheaf should be. 
Surprisingly these analogues are actually closed sets.  
We will describe these domains by a universal property, which when interpreted in the language of scheme theory characterises the affine open subsets of schemes. 

\begin{definition}
	Let $\mathcal{M} (A)$ be the Berkovich spectrum of an affinoid algebra $A$. 
	An ($H$-strict) affinoid domain is a closed subset $V \subset  \mathcal{M} (A)$ together with bounded morphism of ($H$-strict) affinoid domain algebras $f:A \to A_V$ \emph{representing} $V$.
	This means that 
	\begin{itemize}
		\item the image of the induced map $\phi:\mathcal{M} (A_V) \to \mathcal{M} (A)$ is $V$ 
		\item every bounded $K$-Banach algebra morphism $A \to B$ such that the image of $\mathcal{M} (B)$ in $\mathcal{M} (A)$ is contained in $V$ factors in a unique way through $A_V$ \[
	\begin{tikzcd}
		A \ar{rr}{\phi} \ar{dr}& & A_V \ar[dashed]{dl} \\
				& B
	\end{tikzcd}
	.\] 
	\end{itemize}
\end{definition}

Affinoid domains are closed under finite intersections. 
\begin{lemma}\label{lem:intersection_affinoid_domain}
	If $V_1, V_2$ are affinoid domains represented by $A_{V_1}, A_{V_2}$ then $V_1 \cap V_2$ is an affinoid domain represented by $A_{V_1} \widehat\otimes_A A_{V_2}$. 
\end{lemma}
\begin{proof}
	Let $f: A \to B$ be a morphism such that the corresponding morphism  $\phi: \mathcal{M} (B) \to \mathcal{M}(A) $ lands in $V_1 \cap V_2$. In particularly $\im \phi \subset  V_1$ and $\im \phi \subset V_2$. 
	So $f$ factors uniquely through $A_{V_1}$ and $A_{V_2}$.
	Applying \cref{prop:universal_prop_complete_tensor} yields that  $f$ factors unique through $A_{V_1} \cox_A A_{V_2}$ 
	\[
	\begin{tikzcd}
		A \rar \dar & A_{V_1} \dar \ar[bend left]{rdd} \\
		A_{V_2} \rar \ar[bend right]{drr} &  A_{V_1} \cox_A A_{V_2} \ar[dashed]{dr}{\exists !} \\
		 & & B
	\end{tikzcd}
	.\] 
\end{proof}

It is not easy to describe the affinoid domains for a given $\mathcal{M} (A)$ as explicitly as in the case of $\spec$ for rings. 
But there are a few kinds of affinoid domains that ones that will be sufficient to develop the theory. 
\begin{definition}
	Let $A$ be an $K$-affinoid algebra. 
	There are ($H$-strict) \emph{weierstrass domains, laurent domains} and \emph{rational domains}. 
	\begin{description}
		\item[Weierstrass domain] Let $a_1, \ldots, a_n$ be in $A$ and $r_1, \ldots, r_n \in H$. 
			\[
				A\left<r_1^{-1}a_1, \ldots, r_n^{-1}a_n \right> := \frac{a\left<r^{-1}x_1, \ldots, r^{-1}_nx_n \right>}{(x_1-a_1, \ldots, x_n - a_n)}
			.\] 
			Unlike for polynomial rings, this is not an evaluation map. You should think of this as forcing the $a_i$'s to become powerbounded. 
		\item [Laurent domains]
			Let $a_1, \ldots, a_n, b_1, \ldots, b_m \in A$ without common zeroes\footnote{This means that there is no $x \in \mathcal{M} (A)$ that evaluates two or more elements to $0$.} and $r_1,\ldots, r_n$, $s_1, \ldots, s_m \in H$ then 
			\begin{align*}
				A\left<r_1^{-1}a_1, \ldots, r_n^{-1}a_n, s^{-1}_1b_1^{-1}, \right. & \left. \ldots, s^{-1}_mb_m^{-1} \right> \\
				&:= \frac{A\left<r^{-1}_1x_1, \ldots, r^{-1}_nx_n,s^{-1}_1y_1, \ldots,s_m^{-1} y_m  \right>}{(x_1 - a_1, \ldots, x_n - a_n, b_1 y_1 - 1, \ldots, b_m y_m - 1)}
			.\end{align*} 
			This is the affinoid analogue of localization. It makes the $r_i^{-1}a_i$ powerbound and $s_i^{-1}b_i$ invertible and powerbound. 
		\item[Rational domain] With $a_1, \ldots, a_n, a' \in A$ with no common zeros and $r_1, \ldots, r_n \in H$,
			\begin{align*}
				A \left<r_1^{-1}\frac{a_1}{a'}, \ldots, r_n^{-1}\frac{a_n}{a'} \right> := \frac{A\left<r_1^{-1}x_1, \ldots, r_n^{-1}x_n \right>}{(a' x_1 - a_1, \ldots, a' x_n - a_n)}
			.\end{align*}
	\end{description}
\end{definition}

It is clear that Weierstrass domains and Laurent domains are specific types of rational domains. 
These are affinoid domains and the following theorem describes which set $V \subset \mathcal{M} (A)$ they represent. 
\begin{proposition}
	Let $A$ be a ($H$-strict) affinoid ring and $a_1, \ldots, a_n, a' \in A$ without common zero.
	Then the map $A \to A\left<\frac{a_1}{a'}, \ldots, \frac{a_n}{a'} \right>$ represents the domain \[
		\mathcal{M} \left(A \left<r^{-1}_1\frac{a_1}{a'}, \ldots, r^{-1}_n\frac{a_n}{a'}\right> \right) = \{x \in \mathcal{M} (A) \st |a_i|_x \le r_i|a'|, \forall i \in 1, \ldots, n\} 
	.\] 
\end{proposition}
\begin{proof}
	Let's denote the domain as above by $V$. 
	Let $f:A \to B$ be an admissible morphism such that for the reduced morphism $\phi: \mathcal{M} (B) \to \mathcal{M} (A)$ the image $\im \phi \subset  V$.
	Note that because there are no common zeroes, this means that $|a'|_x \ne 0$ for all $x \in V$. 
	So $|f(a')|_{y} \ne 0$ for all $y \in \mathcal{M} (B)$. 
	Hence $f(a')$ is invertible in $B$ by \cref{cor:non_vanish_invertible}. 

	Recall that \[
	A\left<r^{-1}_1\frac{a_1}{a'}, \ldots, r_n^{-1}\frac{a_n}{a'} \right> = \frac{A\left<r_1^{-1}x_1, \ldots, r_n^{-1}x_n \right>}{(a' x_1 - a_1, \ldots, a' x_n - a_n)}
	.\] 

	So to define a map to $B$ that extends the map $f$ from $A$ we need to define the images of $x_i$. 
	We need to be able to quotient this map from by the ideal generated by $a'x_i - a_i$. 
	So its clear that the only way to define this map is like:
	\begin{align*}
		g: A\left<r_1^{-1}x_1, \ldots, r_n^{-1}x_n \right> &\longrightarrow B \\
		x_i &\longmapsto f(a_i) / f(a')
	.\end{align*}
	This is well defined as $f(a')$ is invertible and $|f(a_i) / f(a')|_x = |a_i|_{\phi(x)} / |a'|_{\phi(x)} \le r_i$ as $\phi(x) \in V$. 
	So by \cref{prop:universal_property_tate_algebars} this defines a unique map. 
	By construction $a'x_i - a_i \in \ker g$ for every $i$. Hence this defines a map $A \left<\frac{a_1}{a'}, \ldots, \frac{a_n}{a'} \right>$ as desired. 
\end{proof}

While we do not know what general affinoid domains look like, the following theorem shows that we can get by with just rational domains. 
\begin{proposition}
	[Gerritzen-Grauert Theorem]
	A ($H$-strict) affinoid domain $V \subset  \mathcal{M} (A)$ is a finite union of ($H$-strict) rational domains in $X$.
\end{proposition}
\begin{proof}
	There are many very technical proofs that depend on the theory of rigid geometry (a predecessor of Berkovich geometry).
	The easiest proof and one that is entirely in the language of Berkovich geometry is one by M.\ Temkin \cite{temkinNewProofGerritzenGrauert2005}.
\end{proof}




\subsection{Interlude: $G$-topologies} \label{sec:interlude_g_topologies}

In the next section we will turn $\mathcal{M} (A)$ into a locally ringed space. 
But we will not do this with the canonical topology as defined in \cref{def:spectrum_banach_algebra} (at first). 
In fact the topology that we will use is not a ordinary topology at all. 
It will be a $G$-topology, which is a notion somewhere in between an ordinary topology and a Grothendieck site. 
For a $G$ topology on $X$
the category of opens will still be a collection of subsets of $X$ with inclusion maps, closed under finite intersection (but not union). But the set of covers may be restricted. 
In this section we will follow \cite[][sec. 9.1.]{siegfriedboschNonArchimedeanAnalysisSystematic1984}

\begin{definition}
	[$G$-topology]
	Let $X$ be a set. 
	A $G$-topology $\mathcal{T} $ on $X $ consists of 
	\begin{itemize}
		\item  a collection $S$ of sets in $X$ which are called \emph{admissible opens},
		\item for every admissible open $U \in S$ a set $\cov U$ of \emph{admissible covers} consisting set theoretic covers of $U$ by admissible opens,
	\end{itemize}
	which are subject to the following conditions:
	\begin{enumerate}
		\item $S$ is closed under finite intersections
		\item For any admissible open $U$ is $\{U\}$ and admissible cover of $U$.
		\item If $\{U_i\}_{i \in I} \in \cov U $ and for each $U_i$ there is a cover $\{V_{i, j}\}_{j \in J_i} \in \cov U_i$ then $\{V_{ij}\} _{i \in I, j \in J}$ is an admissible cover of $U$
		\item If  $U, V$ are admissible opens with $V \subset  U$ and given an admissible cover $\{U_i\}_{i \in I} $ of $U$, then $\{V \cap U_i\} _{i \in I}$ is an admissible cover of $V$. 
	\end{enumerate}
\end{definition}
\nomenclature[cov]{$\cov U$}{The set of admissible covers of $U$}
\begin{example}
	The following are some exampels of $G $-topological spaces. 
	\begin{itemize}
		\item Any topological space is a $G$-topological space by letting $S$ be the set of opens and for any open  $U$ define $\cov U$ to be all the set theoretic covers. 
		\item A less obvious $G$-topological space is the following. 
			Let $X$ be any topological space. 
			Let $S$ be the set of closed sets in $X$ and let the admissible covers be the finite set theoretic covers. 
	\end{itemize}
\end{example}
This last example is somewhat related to the topology that we will eventually define on $\mathcal{M} (A)$. 
Most definitions for topological spaces carry straight over to $G$-topological spaces, for example: 
\begin{definition}
	These definitions should not be surprising, but take note how reduced structure of $G$-topologies forces us to be slightly more precise.  
	\begin{itemize}
		\item  Let $X, Y$ be $G$-topological spaces. 
			A function $f: X \to Y$ is called \emph{continuous} if every inverse of an admissible open in $X$ is an admissible open, and every inverse of an admissible cover $\{U_i\} $ of $U$ gives an admissible cover $\{f^{-1}(U_i)\} $ of $f^{-1}(U)$. 
		\item A $G$-topological space $X$ is \emph{compact} if $X$ itself is an admissible open and every admissible cover of $X$ can be reduced to a finite admissible cover. 
		\item A $G$-topological space $X$ is \emph{disconnected} if there is an admissible cover $\{U_i\} _{i \in I}$ of $X$ such that there we can split the index set $I = I_1 \sqcup I_2$  such that \[
				\left(\bigcup_{i \in  I_1} U_i\right)\cap \left( \bigcup_{i \in I_2}  \right)  = \emptyset, \text{ and } \bigcup_{i \in I_1} U_i, \bigcup_{i \in I_2} U_i \text{ are nonempty}
		.\] 
	\end{itemize}
\end{definition}

$G$-topologies contain precisely the right information to define sheafs. 
\begin{definition}
	Let $(X, \mathcal{T} )$ be a $G$-topological space.
	A \emph{presheaf on $X$} with values in a category $\mathcal{C} $ is a functor $\mathcal{F} :S^{\text{op}} \to \mathcal{S} $. 

	A presheaf $\mathcal{F} $ is called a \emph{sheaf} if for any admissible open  $U$ and cover $\{U_i\}_i $ of $U$ the sequence \[
	\begin{tikzcd}
		\mathcal{F} (U) \rar & \prod_{i \in I} \mathcal{F} (U_i) \rar[shift left]\rar[shift right] & \prod_{i, j \in I} \mathcal{F} (U_{i} \cap U_j)
	\end{tikzcd}
	\] 
	is exact. 
\end{definition}
\begin{remark}\label{rem:g_topology_local}
	A $G$ topology on $X$ is not determined locally. 
	For example let $X$ be a topological space and $G_1$ be the ordinary topology and $G_2$ be $G_1$ without the admissible open $X$ and its covers.  
	Then $G_1, G_2$ are the same when restricted to every non-trivial open  $U \subsetneq X$, but $G_1 \ne G_2$. 
	One may impose extra axioms on a $G$ topology to fix this, but this would take us too far outside the scope of this thesis. 
	The curious reader may consult \cite[sec.\ 9.1.2]{siegfriedboschNonArchimedeanAnalysisSystematic1984}.
\end{remark}



\subsection{The structure sheaf on $\mathcal{M} (A)$} \label{sec:the_structure_sheaf_on_ma}

First we need to define a $G$-topology $\mathcal{M} (A)$. 
In this section it does not matter whether we work with strict or $H$-strict or non-strict affinoid algebras. So we will work in the most general case and let all algebras be non-strict unless specified otherwise.  

\begin{definition}
	Let $A$ be an affinoid algebra. 
	The \emph{$G$-topology} on $\mathcal{M} (A)$ is the topology where the admissible opens are the affinoid domains and the covers are finite set theoretic covers of affinoid domains. 
\end{definition}

We can define a presheaf $\mathcal{O}_X$ on $X =\mathcal{M} (A)$ with the $G$-topology by defining $\mathcal{O}_X(V) = \mathcal{A} _V$ for any affinoid domain $V$ represented by $\mathcal{A}_V$.
The restiction maps are given by the defining property of affinoid domains.

This presheaf turns out to be a sheaf, which will follow from the following theorem. 
\begin{theorem}[Tate's acyclicity theorem]\label{thm:tate_acyclicity}
	Let $X = \mathcal{M} (A)$ and $\{V_i\} $ be an admissible cover of $X$. 
	Then for any finite banach $A$ module, $M$ the Čech complex \[
		0 \to M \to \prod_{i} M \cox_A A_{V_i} \to \prod_{i, j} M \cox_A A_{V_i} \cox_A A_{V_j} \to \ldots
	\] 
	is exact. 
\end{theorem}
\begin{proof}
	For a full proof see \cite[][prop.\ 2.2.5]{berkovichSpectralTheoryAnalytic2012}. 
	The entire proof boils down to reducing this to the case of a Laurant covering $A\left<f \right>, A\left<f^{-1} \right>$ of $A$ for some $f \in A$. and showing that \[
		0 \to A \to A\left<f \right>\times  A\left<f^{-1} \right> \to A\left<f, f^{-1} \right> \to 0
	.\]  
	is exact. 
\end{proof}


\begin{corollary}
	The presheaf $\mathcal{O}_X$ is a sheaf on the $G$-topology of $X$.
\end{corollary}
\begin{proof}
	Let $V$ be an affinoid domain and $\{V_i\} $ a finite cover. 
	Taking $M = A_V$ in \cref{thm:tate_acyclicity} yields \[
	0 \to A_V \to \prod_{i } A_V \otimes_A A_{V_i} \to \prod_{i,j} A_V \otimes A_{V_i} \otimes A_{V_j}
	.\] 
	Rewriting each term yields that \[
	0 \to A_V \to \prod_i A_{V_i} \to \prod_{i, j} A_{V_i \cap V_j}
	\] 
	is exact. This is exactly the sheaf condition. 
\end{proof}

The $G$-topology and the structure sheaf can be slightly refined to allow finite unions. 
\begin{definition}
	Let $X = \mathcal{M} (A)$ for some $K$-affinoid algebra $A$. 
	A set $V\subset  X$ is \emph{special} if it is a finite union of affinoid domains. 
	We write $S(X)$ for the set of \emph{special sets} on $X$. 
\end{definition}

\begin{definition}
	$S(X)$ with finite covers defines a $G$-topology on $X$. 
	The structure sheaf  $\mathcal{O}_X$ on $X$ can be extended to a sheaf on $S(X)$ by defining \[
		\mathcal{O}_X(V) = \ker\left(\prod_i A_{V_i} \to \prod_{ij} A_{V_{ij}}\right)
	.\] 
\end{definition}


This structure sheaf can also be used to define a structure sheaf on the canonical topology as well. 
\begin{definition}\label{def:structuresheaf_cannonical_topology}
	Let $X = \mathcal{M} (A)$. Then we can define a sheaf on $\mathcal{O}_X$ on $X$ via \[
		\mathcal{O}_X\left( U \right)  = \varprojlim_{V \subset U} \mathcal{O}_X(V)
	\]   
	where $V$ runs over all the special sets.
\end{definition}
This turns $X$ into a locally ringed topological space. 
It is a grave abuse of notation to use $\mathcal{O}_X$ for both the structure sheaf on the $G$-topology of $X$ as well as the canonical topology. 
It is important keep in mind that there are two topologies with their respective structure sheaf, namely a locally ringed space $(X, \mathcal{O}_X)$ and a locally ringed $G$-topological space $(X_G, \mathcal{O}_{X_G})$. 

\nomenclature[OX]{$\mathcal{O}_X$}{The structure sheaf on $X$}
\nomenclature[OXG]{$\mathcal{O}_{X, G}$}{The structure sheaf on the $G$-topology of $X$}


\subsection{Gluing Berkovich spectra to $K$-analytic spaces} \label{sec:gluing_berkovich_spectra_to_k_analytic_spaces}


The Berkovich spectra of ($H$-strict) $K$-affinoid algebras can be glued together to obtain ($H$-strict) $K$-analytic spaces, similar to how schemes are made out of spectra of rings. 
However, this is not as straightforward as the definition of a scheme. 
The culprit is that $G$ topologies do not glue together uniquely by \cref{rem:g_topology_local}. 
The solution for this to define a general $K$-analytic space with an atlas and then refine this atlas to a maximal atlas, similar to how one might introduce a smooth manifold in a first differential geometry course. 

The idea is to define a general  $K$-analytic space, by starting with a locally Hausdorff topological space $X$, and covering it with a suitable set cover $\{V_i\} _{i}$ of compact Hausdorff spaces, each identified with some affinoid domain $\mathcal{M} (A_{V_i})$, such that when $V_j \subset  V_i$, $ \mathcal{M} (A_{V_j})$ is an affinoid subdomain of $\mathcal{M} (A_{V_j})$. 
Using this description we can obtain a $G$-topology of affinoid domains corresponding structure sheaf $\mathcal{O}_{X, G}$.  
The details of this construction are very technical and it would be outside the scope of this thesis. 
A good overview is given in \cite[chap.\ 5]{conrad2008several}.

On a special type of $K$-analytic spaces we can also obtain a structure sheaf for the ordinary topology. 
These spaces are called \emph{good} and are defined as follows. 
\begin{definition}
	A $K$-analytic $X$ space is \emph{good} if every point $x \in X$ has neighborhood isomorphic to $\mathcal{M} (A)$ for some affinoid algebra $A$. 
\end{definition}
For general $K$-analytic spaces the only requirement is that a finite union of affinoid domains containing $x$ is a neighborhood of $x$. 




