\documentclass[a4paper]{article}
\input{../preamble.tex}

\title{Mid year report: Berkovich Geometry}

\begin{document}

\maketitle

\tableofcontents

\pagebreak


\todototoc
\listoftodos
\pagebreak


\section{Introduction} \label{sec:introduction}

A powerful tool to study complex varieties is the analytification functor, which turns a  smooth variety over $\C$ into a complex manifold, that can be studied using analytic methods. 
Other rings that are well suited for analysis are the $p$-adic fields $\Q_p$ or more generally non-archimedean fields. 
So the question arises whether a similar analytification functor can be constructed for  varieties over non-archimedean fields. 

Tate's answer was the theory of rigid spaces as suitable analytic spaces. 
But they have various topological problems that makes them less than ideal for the task. 
For example they are totally disconnected. To solve these problems Tate restricted the set of open covers on these spaces. 

Berkovich proposed another approach by adding many more points to the rigid space to resolve various problem. 
The resulting topological spaces are very well behaved. 
For example, for connected proper schemes they are path connected and compact. 
Even more, the analytification of a curve has the structure of a profinite real graph. 

For the thesis the main interest is not to do analysis on Berkovich spaces of varieties, but rather to study the relation between the Berkovich space of a curve and its semi-stable models as outlined in \cite{bakerStructureNonarchimedeanAnalytic2013}.

This text is a based on various roughly analogous introductory text on Berkovich geometry \cite{bakerarizona,temkinIntroductionBerkovichAnalytic2010,nicaiseNONARCHIMEDEANGEOMETRY,boschLecturesFormalRigid2014} as well as Berkovich's first paper on the subject \cite{berkovichSpectralTheoryAnalytic2012}.
When another source is used it will be explicitly pointed out in the text. 

\section{Basic valuation theory} \label{sec:basic_valuation_theory}

\input{chapters/valuations.tex}

\section{Berkovich spaces of rings} \label{sec:berkovich_spaces}
\input{chapters/spectra_of_rings.tex}


\section{$K$-analytic spaces} \label{sec:K_analytic_spaces}
\input{chapters/affinoid.tex}


\section{$K$-analytic spaces from algebraic objects} \label{sec:berkovich_analytification_of_schemes}
\input{chapters/analytification.tex}


\section{Analytification of Curves} \label{sec:analytification_of_curves}
\input{chapters/curves.tex}


\section{What comes next} \label{sec:what_comes_next}

Use the reduction map and Reynaud's theory on formal schemes to understand the relation to the analytification of a proper smooth curve and its semistable models. 


\pagebreak
\todo{Check whether all these citations are correct}
\printbibliography
\end{document}
