On rings like $\Z$ and $\Q$ and $\C$ the absolute value function gives away of measuring how low \emph{large} each element is. 
We can axiomatize proterties of an absolute value function and look for them on arbitrary rings. 
These types of functions are called (semi)norms, absolute values or valuations, depending on the specific propreties and context.  
\begin{definition}
	Let $R$ be a ring. A \emph{absolute value on $R$} is a function $|\cdot |: R \to \R^{+} \cup \{0\} $ satisfying for all $a, b \in R$
	\begin{enumerate}
		\item $|a| = 0 \iff a = 0$ 
		\item $|a \cdot b| = |a| \cdot |b|$ 
		\item $|a + b| \le |a| + |b|$
	\end{enumerate}
\end{definition}
Note that $R$ is not the zero ring, then $|1| = 1$ because $|1|^2 = |1| $ and $|1|\ne 0 $. 
\begin{example}
	The usual definition of absolute value on $\Z, \Q, \R$ is an absolute value. 
\end{example}
\begin{example}
	On any integral domain we can define the trivial absolute value as \[
	 |a| = \begin{cases}
		 1 & a \ne 0 \\
		 0 & a = 0
	 \end{cases}
	.\] 
\end{example}
\begin{example}
	A weirder absolute value on $\Z$ is the \emph{$p$-adic absolute value}, where $p$ is a prime. 
	Its defined as $|a|_p = p^{-n}$ where $n$ is the largest integers such that $p^{n} \divides a$, if $a \ne 0$ and $|0|_p = 0$. 


	This $p$-adic absolute value can be extended to an absolute value on $\Q$ by defining $|a / b|_p = \frac{|a|_p}{|b|_p}$. Let $\frac{a}{b}$ be any fraction. 
	I like to think about this in the following way. 
	Factor out the largest powers of $p$ out of $a$ and $b$ and write $a = p^{n} a', b = p^{m} b'$. Then $\frac{a}{ b} = p^{n - m} \frac{a'}{ b'}$ and $|a / b|_p = p^{m - n}$. 
	So the $p$-adic absolute values only cares about what powers of $p$ occur and doesn't care about numbers coprime to $p $.
\end{example}
As we will see in \cref{sec:the_berkovich_spectrum_of_z}, we have esssentially listed all absolute values on $\Z$ and $\Q$ as examples above.  

\begin{proposition}
	A ring $R$ with an absolute value is a metric space with metric $d(x, y) = |x - y|$. 
\end{proposition}
\begin{definition}
	A ring $R$ with absolute value is \emph{complete} if all Cauchy sequences are covergent. 
\end{definition}
\begin{definition}
	Any ring $R$ with absolute value can be completed, which is defined as \[
		\widehat{R} = \{(a_n)_n \text{ Cauchy sequence in } R\} / \sim
	\] 
	where two sequence $(a_n)_n, (b_n)_n$ are equivalent if $(a_n - b_n)_n \to 0$ as $n \to \infty$.
	Given  $a, b \in R$ with representivis $(a_n)_n, (b_n)_n$, the addition and multiplication are defined as $a + b = [(a_n + b_n)], a\cdot b = [(a_n \cdot b_n)]$. 
\end{definition}

Absolute values are a special case of (semi)norms
\begin{definition}
	Let $R$ be any ring. A \emph{seminorm on $R$} is a function $|\cdot |: R \to \R^{+} \cup \{0\} $ satisfying for all $a, b \in R$ 
	\begin{enumerate}
		\item $|0| = 0, |1| = 1$ 
		\item $|a \cdot b| \le |a| \cdot |b|$  (submultiplicativity)
		\item $|a + b| \le |a| + |b|$ (triangle inequality)
	\end{enumerate}
	A seminorm is called \emph{multiplicative} if it also satisfies a stronger version of 2. 
	\begin{enumerate}
		\item [4.]  $|a \cdot  b| = |a| \cdot |b|$
	\end{enumerate}
\end{definition}
Sometimes we will stress the fact that a (semi)norm might not be multiplicative and call it a \emph{submultiplicative norm}. 

\begin{lemma}
	If $|\cdot |$ is a multiplicative seminorm on $R$ then  $|a | = |-a|$ for all $a \in R$. 
\end{lemma}
\begin{proof}
	We have $|a|^2 = |a^2| = |-a|^2$. As all norms are positive we find that $|a| = |-a|$. 
\end{proof}


\begin{definition}
	The \emph{kernel} of a seminorm $|\cdot |: R \to \R^{+}$ is defined as \[
		\ker(|\cdot |) = \{a \in \R \st |a| = 0\} 
	.\] 
\end{definition}
\begin{remark}\label{rem:ker_norm_ideal}
	Let $ |\cdot |$ be a norm on $R$. Then $\ker |\cdot |$ is an ideal of $R$. If $|\cdot |$ is multiplicative then $\ker |\cdot |$ is even a prime ideal!
\end{remark}
\begin{proof}
	Let $a, b \in \ker |\cdot |, c \in R$. Then $0 \le |a + b| \le |a|+|b| = 0$. So  $a + b \in \ker |\cdot |$. 
	Also $0 \le |c \cdot a| \le |c|\cdot |a| = 0$. So $c \cdot a \in \ker |\cdot |$. 
	This shows that $\ker |\cdot  |$ is an ideal. 
	
	Suppose that $|\cdot |$ is multiplicative. 
	Let $a, b\in R $ such that $a\cdot b \in \ker |\cdot |$ then  $|a|\cdot |b| = |a\cdot b| = 0$. 
	Hence either $|a| = 0$ or  $|b|=0$. 
	So either  $a \in \ker |\cdot |$ or $b \in \ker |\cdot |$. 
\end{proof}

In some sense seminorms are analogous to ideals and and multiplicative seminorsm are analogous to prime ideals. This is will be the basis of Berkovich spectra of rings.
Like the ordinary $\spec$ functor we can define the space of all multiplicative norms on a ring. 
Unfortunately you can't just copy all constructions we know for $\spec$. 
For example, we can't define a Zarisky topology on this set. 
In fact we will need two different topologies on this space for the theory to work. 
Don't worry, this is a feature, not a bug. 
One topology will have all the nice properties you can think of: Haussdorf, compact, path-connected, locally contractible, \ldots while the other one is great for sheaf theory. 


\begin{definition}
	Let $R$ be a ring and $|\cdot |$ a seminorm on $R$. 
	Then $|\cdot |$ is called a \emph{norm} if $\ker |\cdot | = 0$, i.e.\ $|a| = 0 \iff a = 0$. 
\end{definition}

So an absolute value is a multiplicative norm. 

\begin{lemma}
	Any seminorm $|\cdot |$ on a field $F$ is a norm, i.e.\ has trivial kernel. 
\end{lemma}
\begin{proof}
	We have that $|1| = 1$. So $1 \not\in \ker |\cdot |$ and thus $\ker |\cdot |$ is an ideal of $F$ different from $F$. 
	As $F$ is a field this means that $\ker |\cdot | = (0)$. So $|\cdot |$ is norm. 
\end{proof}

\subsection{Non-Archimedean rings and fields} \label{sec:non-archimedean_rings_and_fields}
\begin{definition}
	A (semi)norm $|\cdot |$ on $R$ is called \emph{non-archimedean} if it satisies the following stronger version of the triangle inequality, \[
	\forall a, b \in \R: |a + b| \le \max \{|a|, |b|\} 
	.\] 

	Confusingly a \emph{Archimedean (semi)norm} is a norm that is not non-archimedean.
\end{definition}

\begin{definition}
	A \emph{non-archimedean ring} (resp.\ \emph{field}) is a ring (resp.\ field) equipped with multiplicative non-archimedean norm. 
\end{definition}

\begin{exercise}[\cite{nicaiseNONARCHIMEDEANGEOMETRY}]
	Let $k$ be a field.
	Show that a multiplicative seminorm $|\cdot |$ on $k$ is non-archimedean if and only if the image of $\Z$ in $k$ is bounded. 
\end{exercise}
\begin{proof}
	Suppose $|\cdot |$ is non-archimedean. Then for any positive integers $n$ we have \[
	|n| = \left|\sum_{i = 1}^{n} 1 \right| \le \max \{1, 1, \ldots, 1\}  = 1
	.\] 
	And for negative integers we have $|n| = |-n| \le 1$. So $\|\cdot \|$ is bounded on the image of $\Z$ by $1$. 


	Suppose that $|\cdot |$ is bounded on the image of $\Z$ by $c$. 
	Let $x, y \in k$. Then \[
		|(x + y)^{n}| = \left| \sum_{i = 0}^{n} \binom{i}{n} x ^{i} y ^{n-i}\right| \le (n + 1)\cdot c \max(x, y)^{n}
	.\] 
	So \[
		|x + y| \le \sqrt[n]{c\cdot (n + 1)}  \max(x, y)
	.\] 
	Taking $n \to \infty$ yields the non-archimedean triangle inequality. 
\end{proof}

\begin{corollary}
	Let $A \subset  B$ an inclusion of rings  equipped with multiplicative norms such that the norm on $B$ extends the norm on $A$. 
	Then $A$ is non-archimedean if and only if $B$ is non-archimedean. 
\end{corollary}

\begin{remark}
	Suppose $R$ is a multiplicative non-archimedean norm and we have $a, b \in R$ such that $|a| \ne |b|$ then the triangle inequality is an equality \[
	|a + b| = \max \{|a|, |b|\} 
	.\] 
	So in some sense equality is the generic case. 
\end{remark}
\begin{proof}
	Suppose without loss of generality that  $|a| > |b|$, and assume by contradiction that $|a + b| < \max \{|a|, |b|\}  = |a|$. 
	Then \[
		|a| = |(a + b) - b| \le \max \{|a + b|, |- b|\} = \max \{|a + b|, |b|\}  
	.\] 
	But this contradicts that $|a| > |b|$ and $|a| > |a + b| $. 
\end{proof}
The non-archimedean triangle inequality sounds like a really strong property and thus it might seem that not many norms will be non-archimedean. 
But as you will see in this thesis, most norms that pop up are non-archimedean. 
In fact the only complete valued fields with archimedean norms are $\R$ and $\C$.\footnote{This is a consequence of Gel'fand-Mazur theorem and Ostowki's classification (see \cref{thm:ostrowksi}) of norms on $\Q$.}



Note that the definition a non-archimedean norm only depends on the multiplicative structure on $\R^{+}$ and no longer depends on the additive structure. 
Sometimes it is more natural define norms in terms the isomorphic group $\R, +$ (and add $\infty$ instead of $0$ to the group). 
These are typically called valuations. 


\begin{definition}
	Let $R$ be a ring. A \emph{valuation on $R$} is a function $v:R \to \R \cup \{\infty\} $ such that 	
	\begin{itemize}
		\item $v(0) = \infty$, $v(1) = 0$. 
		\item $v(a\cdot b) = v(a) + v(b)$
		\item $v(a + b) \le \min\{v(a), v(b)\}$
	\end{itemize}
\end{definition}

\begin{remark}
	Note that there is essentially no difference between a non-archimedean absolute value and a valuation because because they are in bijective correspondence with one another.  For absolute value $|\cdot |$ defines a valution $x \mapsto -\log |x|$ and given a valution $v$ one defines a non-archimedean absolute value $x\mapsto e^{- v(x)}$. 
\end{remark}





\begin{theorem}\label{thm:norm_finite_field_ext}
	If $L$ is a finite field extension of a complete non-archimedean field $K$, then there is a unique extension of the norm of $K$ to $L$ and this extension is also non-archimedean.
\end{theorem}
\begin{proof}
	This a very technical result and for the proof we refer to \cite[][appendix A]{boschLecturesFormalRigid2014}. 
\end{proof}

\begin{corollary}
	If $K$ is a complete non-archimedean field then the norm of  $K$ extends uniquely to its algebraic closure $\overline{K}$.
\end{corollary}
\begin{proof}
	Recall that \[
	\overline{K} = \varprojlim_{L \supset K} L
	.\] 
	where $L$ ranges over all algebraic extensions of $K$. 
	As all these algebraic extensions have unique norms extending  the norm on $K$ and for $L_1 \supset L_2 \supset K$ the norm on  $L_1$ must restrict to norm on $L_2$ by uniqueness, it is clear that the norm functions $L \to \R^{+}$ glue to a map $\|\cdot \|: \overline{K} \to \R^{+}$. 

	It is easy to verify that this is a norm on $\overline{K}$ extending the norm on $K$. 
\end{proof}

\begin{theorem}
	[Krasner's Lemma]
	Let $K$ be a non-archimedean algebraically closed field. 
	Then its completion, $\widehat K$ is algebraically closed as well. 
\end{theorem}
\begin{proof}
	This follows from the continuity of roots. See \cite[][lem A.6]{boschLecturesFormalRigid2014} for a detailed argument. 
\end{proof}

This show that we can cannonically turn any non-archimedean field $K$ into an algebraically closed and complete field in a cannonical way by considering $\widehat{\overline{K}}$, which is first taking the algebraic closure of $K$ and then completing it. 

\begin{definition}
	For a prime $p$ we define the \emph{p-adic complex numbers} as \[
	\C_p = \widehat{\overline{\Q_p}}
	.\] 
\end{definition}

This is useful because Berkovich geometry works best when the base field is algebraically closed and complete. 

\begin{definition}
	Let $R$ be a non-archimedean ring. Then we write 
	\begin{align*}
		R^{o} &= \{a \in k \st |k| \le 1\}  \\
		R^{oo} &=  \{a \in k \st |k| < 1\}  \\
		\widetilde R &= R^{o} / R^{oo}
	.\end{align*}
\end{definition}
If $k$ is a field then $k^{0}$ is a valuation ring and $ k^{00}$ is its maximal ideal. 

We will useally write $K$ for a non-arcimedean field, $R = K^{0}$ for its valuation ring, $k = \widetilde K$ for its residue field. 

\begin{definition}
	Let $K$ be a non-archimedean field. 
	The \emph{value group of $K$} is \[
	|K^{\times }| = \{|a| \st  a \in K^{\times }  \} 
	.\] 
	This is a subgroup of $(\R^{ +}, \cdot )$. 
\end{definition}


\subsection{Ultrametric spaces} \label{sec:ultrametric_spaces}

\begin{definition}
	A \emph{ultrametric space} is a topological spaces $(X, d)$ where the metric satisfies the non-archimedean triangle inequality. 
	\[
		d(x, y) \le \max \{d(x, z) ,d(z, y)\}, \quad \forall x, y ,z \in X
	.\] 
\end{definition}
\begin{exercise}
	If $d(x,z) \ne d(z,y)$ the inequality is an equality. 
\end{exercise}
\begin{proof}
	Suppose without loss of generality that $d(x, z) \ge d(z,y)$, so $d(x, y) \le \max \{d(x, z), d(z,y)\} = d(x, z) $. 
	Then $d(x, z) \le \max \{d(x, y), d(y,z)\}$. So $d(x, z) \le d(x, y) \le d(x, z)$. So we find equality.
\end{proof}
\begin{corollary}
	Any point of a ball (open or closed) is a center for that ball. 
\end{corollary}
\begin{corollary}
	If two balls have non-empty intersection that one must be included in the other. 
\end{corollary}
\begin{corollary}
	The topology of $X$ is totally disconneced. 
\end{corollary}

Non-archimedean fields are ultrametric spaces with the metric $d(x, y) = |x - y|$. 

